A Switching Planner for Combined Task and Observation Planning

### 2011-05-03 code/subarchitectures/planner.sa/trunk/src/latex/AAAI11/aaai11.tex
remove comma

\special{! /pdfmark where
{pop} {userdict /pdfmark /cleartomark load put} ifelse
[ /Author (Moritz Goebelbecker, Charles Gretton, Richard Dearden)
/Title (A Switching Planner for Combined Task and Observation Planning)
/Subject (Proceedings of the Twenty-Fifth Conference on Artificial Intelligence)
/Keywords (planning under uncertainty)
/DOCINFO pdfmark
userdict /pdfmark /cleartomark load put}

@@

\title{A Switching Planner for Combined Task and Observation Planning}
\author{
Moritz G{\"o}belbecker \\ Albert-Ludwigs-Universit{\"a}t Freiburg, Germany\\
goebelbe@informatik.uni-freiburg.de
\And
Charles Gretton, Richard Dearden,\\
University of Birmingham, United Kingdom\\
\{c.gretton,R.W.Dearden\}@cs.bham.ac.uk} 
\setcounter{secnumdepth}{0}

>>>>

\special{! /pdfmark where
{pop} {userdict /pdfmark /cleartomark load put} ifelse
[ /Author (Moritz Goebelbecker, Charles Gretton, Richard Dearden)
/Title (A Switching Planner for Combined Task and Observation Planning)
/Subject (Proceedings of the Twenty-Fifth Conference on Artificial Intelligence)
/Keywords (planning under uncertainty, continual planning, robot planning)
/DOCINFO pdfmark
userdict /pdfmark /cleartomark load put}

@@

\title{A Switching Planner for Combined Task and Observation Planning}
\author{
Moritz G{\"o}belbecker \\ Albert-Ludwigs-Universit{\"a}t Freiburg, Germany\\
goebelbe@informatik.uni-freiburg.de
\And
Charles Gretton, Richard Dearden\\
University of Birmingham, United Kingdom\\
\{c.gretton,R.W.Dearden\}@cs.bham.ac.uk} 
\setcounter{secnumdepth}{0}
